### 2017-02-28 2017mergingmerges/section/XX-Proof.tex
proof: talk about subset of fused heap

The @Soundness@ theorem above uses @EvalBs@ to evaluate the fused program: if it evaluates to stream @ss@ and heap @h@, then @EvalOriginal@ ensures that the original program evaluates with that program's subset of the heap.

>>>>

The @Soundness@ theorem above uses @EvalBs@ to evaluate the fused program, and @EvalOriginal@ ensures that the original program evaluates with that program's subset of the fused heap.
%%% AR: Really would like to say something about this but no room to explain properly
% For shared inputs when one program has pulled, the other program must be evaluated with the other value removed from the end of the stream.
